Problem Set 3 (Answers)

### 2019-10-12 static/homeworks/03-problem-set-answers.Rmd
Update answer key 3 graph

slope_simulations %>%
  ggplot(data = .)+
  aes(x = stat)+ # slope from simulations
  geom_histogram(color = "white", # the histogram
                 fill = "indianred")+
  # add vertical line for our sample slope
  geom_vline(xintercept = sample_slope,
             color = "red",
             size = 2)+
  # add label
  geom_label(x = sample_slope,
             y = 200,
             color = "red",
             label = expression(paste("Our ", hat(beta[1]))))+
  # add "shading" for p-value's two sides
  # right side
  geom_rect(xmin=68.798,
            xmax=100,
            ymin=0,
            ymax=300,
            color = "red",
            alpha=0.5)+
  # left side
  geom_rect(xmin=-100,
            xmax=-68.798,
            ymin=0,
            ymax=300,
            color = "red",
            alpha=0.5)+
  scale_x_continuous(seq(-75,75,25))+
  labs(x = expression(paste("Distribution of ", hat(beta[1]), " under ", H[0], " that ", beta[1]==0)),
       y = "Samples")+
    theme_classic(base_family = "Fira Sans Condensed",
           base_size=20)
```

>>>>

slope_simulations %>%
  ggplot(data = .)+
  aes(x = stat)+ # slope from simulations
  geom_histogram(color = "white", # the histogram
                 fill = "indianred")+
  # add "shading" for p-value's two sides
  # right side
  geom_rect(xmin=68.798,
            xmax=100,
            ymin=0,
            ymax=450,
            fill = "pink",
            alpha=0.4)+
  # left side
  geom_rect(xmin=-100,
            xmax=-68.798,
            ymin=0,
            ymax=450,
            fill = "pink",
            alpha=0.4)+
  # add vertical line for our sample slope
  geom_vline(xintercept = sample_slope,
             color = "red",
             size = 2)+
  # add label
  geom_label(x = sample_slope,
             y = 200,
             color = "red",
             label = expression(paste("Our ", hat(beta[1]))))+
  scale_x_continuous(breaks=c(-75,-50,-25,0,25,50,75),
                     limits=c(-75,75),
                     expand=c(0,0))+
  scale_y_continuous(limits=c(0,450),
                       expand=c(0,0))+
  labs(x = expression(paste("Distribution of ", hat(beta[1]), " under ", H[0], " that ", beta[1]==0)),
       y = "Samples")+
    theme_classic(base_family = "Fira Sans Condensed",
           base_size=20)
```
